### 2024-09-14 Response/Response.tex

\section{Conclusion}
In this paper, we studied a three-tier WPMEC system that is consisting of edge and cloud servers as well as WDs. We first proposed a harvest-then-offload mechanism that efficiently schedules the computing resources and allocates the wireless energy. This is achieved by formulating an optimization problem that aims to minimize the ET's energy transmission while satisfying the tasks computation deadline. We then proposed a matching algorithm called WiEnTM that optimally solves the aforementioned problem. We further proposed a parallel implementation of this algorithm with nearly logarithmic complexity. We also investigated the performance of WiEnTM through numerical experiments. Our results show a significant reduction in ET's transmitted energy compared to different offloading policies. \textcolor{blue}{Our algorithm also requires up to 34\% less overall ET's energy transmission compared to an existing work in the literature.}

For future work, we will consider the dynamic behavior of three-tier WPMEC system and propose an online learning approach to achieve the optimal decisions under uncertainty. \textcolor{blue}{We will also study more powerful WDs with full-duplex capability in future.}

\bibliographystyle{IEEEtran}
\bibliography{references}

\title{Responses to the Reviewers' Comments}

\maketitle

\vspace{-1.5cm}
\setstretch{1.6}

\setcounter{page}{1}

\begin{itemize}
	\item \textbf{Title of Manuscript}: A QoE-Oriented Computation Offloading Algorithm based on Deep Reinforcement Learning for Mobile Edge Computing

	\item \textbf{Authors}:  Iman Rahmati, Hamed Shah-Mansouri, and Ali Movaghar

	\item \textbf{Affiliation}: Departments of Electrical Engineering and Computer Engineering,  Sharif University of Technology, Tehran, Iran

	\item \textbf{Paper Reference Number}: TNSE-2024-03-0468

\end{itemize}

\vspace{0.3cm}

\setstretch{1.2}

\noindent We would like to express our gratitude to the reviewers for their valuable recommendations toward improving the quality of our paper. We also want to gratefully thank the associate editor for handling the paper. Our responses to the reviewers' comments are given below. For convenience, we have used blue font for the revised or newly added paragraphs in the manuscript.\newline

\setcounter{section}{0}
\renewcommand*{\thesection}{\Roman{section}}
\makeatletter

\newpage

\section{Response to Reviewer 1}
\begin{enumerate}

\item \underline{Reviewer's Comment}: 
\textit{``Lots of the studies focus on the research on resource optimisation of MEC by DRL, it is expected to survey the state-of-the-art within 3 years, and summarise it as an individual section, departing from the Section of Introduction. Besides, the existing related work only has one paragraph without any discussion about the pros/cons of the previous work.''} \newline

\underline{Authors' Reply}:\\

Ref

\item \underline{Reviewer's Comment}: 
\textit{``Please highlight what and how the proposed approach provides "high performance" to further specify the motivations and contributions. Especially, please highlight the reason why the authors design the framework by integrating LSTM. Otherwise, it will make the innovations seem weak.''} \newline

\underline{Authors' Reply}:\\

\item \underline{Reviewer's Comment}: 
\textit{``In section III, why is the size of the task selected from a discrete set? Is it selected randomly or in another way? Besides, the authors define the offloading indicate function as $y_{i,j}(t$, it should be involved when modelling the Edge Execution phrase.''} \newline

\underline{Authors' Reply}:\\

\item \underline{Reviewer's Comment}: 
\textit{``Some sota methods (e.g., DDQN, DDPG) are expected to be compared in the section on performance evaluation, and authors should have more discussions about the evaluation results rather than merely introducing them. Besides, I think it is better to design the evaluations with a real dataset. Besides, 9\% and 6\% are not significant improvements compared to other methods.''} \newline

\underline{Authors' Reply}:\\

\item \underline{Reviewer's Comment}: 
\textit{``Other concerns are also expected to be addressed: (a) be careful to use words like "battery level" to express the energy consumption, because some of the energy is provided by the wired line power. (b) Most of the references are out of 3 years, please investigate more studies published in recent years. (c) The authors should thoroughly check the writing style, grammar, and spelling to enhance the paper's clarity, conciseness, and overall impact.''} \newline

\underline{Authors' Reply}:\\

Ref

\end{enumerate}

\newpage

\section{Response to Reviewer 2}
\begin{enumerate}

	\item \underline{Reviewer's Comment}: 
	\textit{``The authors should provide a comparative table to highlight their contributions. Specially, the authors should compare their method with other references on computation task offloading cited in the paper, including aspects such as scenarios, methods, advances, drawbacks, and so on.''} \newline

	\underline{Authors' Reply}:\\
	Ref

	\begin{table*}[htbp]\textcolor{blue}{
			\renewcommand{\arraystretch}{0.7}
			\captionsetup{name=TABLE}
			\caption{Comparison of Related Works}
			\scalebox{0.7}{%
				\begin{tabular}{ lp{2.3cm}p{4.5cm}p{5cm}p{1.5cm}p{3cm}p{5cm}l} 
					\toprule
					\textbf{Paper} & \textbf{Scenario} &  \textbf{Problem} &  \textbf{Objective} &  \textbf{Model} & \textbf{Algorithm/Methods} &  \textbf{Drawbacks}  \\ \midrule
					\cite{huang2019deep} & Wireless-powered MEC & Computation offloading and resource allocations & Maximize computation rate & MIP & DQN & Not consider delay-sensitive tasks \\\midrule
					\cite{Bolourian-WCL24} & MEC with EH devices& Energy harvesting  computation offloading & Minimize drop rate and energy consumption. & MDP  & Deep Q-Learning & \\\midrule
					\cite{zhao2019deep} & MEC & Wireless channels competition & Optimize downlink utility & MDP & Multi-agent D3QN & \\\midrule
					\cite{9253665} &  MEC &  Computation offloading & Minimize drop rate and computation delay. & MDP & D3QN + LSTM & Not consider system energy consumtion\\\midrule
					\cite{sun2024hierarchical} & MEC & Computation offloading and service caching & Minimize average service delay & MDP & hierarchical DRL & Not consider system energy consumtion \\\midrule
					\cite{dai2020edge} & MEC & Resource allocation and computation offloading & Minimize energy consumption & MDP & DDPG & \\\midrule
					\cite{huang2021deadline} & MEC & Computation offloading & Minimizing total energy consumption & POMDP & DDPG & \\ \midrule
					\cite{liu2021learn} & MEC & Resource allocation and computation offloading & Minimize execution cost & POMDP & MADRL &  Not consider delay-sensitive tasks \\\midrule
					\cite{zhou2021deep} & MEC & Resource allocation and computation offloading & Minimize energy consumption of the entire system & MDP & DDQN & Only for a singel MEC system model \\\midrule
					\cite{gao2022large} & heterogeneous MEC & Decentralized computation offloading & Optimize system cost and completion rates & MDP & Multi-agent DDPG & Not take MD's demans into consideration \\\midrule
					\cite{gong2022edge} & MEC-based IIoT & Resource allocation and computation offloading & Minimize task computation delay and energy consumption & MDP & DRL & Not take MD's demans into consideration\\\midrule
					\cite{liao2023online} & MEC & Online computation offloading & Minimize computation delay and energy consumption & MDP & DDQN & Only for a singel MEC system model  \\\midrule
					\cite{wu2023multi} & MEC-based IIoT & Computation offloading & Optimize delay and energy consumption & POMDP & Multi-agent DQN& \\\midrule
					\cite{wu2023computation} & SDN-based MEC & Stochastic game-based resource allocation & Minimize energy consumption and processing delay & MDP & MARL & \\\midrule
					\cite{wu2024privacy} & MEC-based IIoT  & Joint power allocation and computation offloading  & Optimization of privacy protection and quality of service. & MDP & Multi-agent DDPG & \\\midrule
					\cite{wu2024combining} & MEC-based IIoT & Privacy aware computation offloading & Optimization of computation rate and energy consumption & MDP & DDPG  & \\\midrule
					QECO &  MEC &  Computation offloading & Maximize the QoE of each MD individually &MDP & D3QN + LSTM & \\
					\toprule
			\end{tabular}}
			\label{table}}
	\end{table*}

	\newpage
	\item \underline{Reviewer's Comment}: 
	\textit{``I think more explanations should be added for the QoE function. How can the defined function reflect QoE?''} \newline

	\underline{Authors' Reply}:\\
	\newpage
	\item \underline{Reviewer's Comment}: 
	\textit{``(a) What inputs and outputs of Algorithm 2? (b) They should be added to make readers clearly understand the results.''} \\\newline
	\underline{Authors' Reply}: (a) To address the reviewer concern about algorithm 2, we have revised secound paragraph of subsection (Training Process Algorithm at EN $j \in \mathcal{J})$ in Section IV to clarify the inputs and outputs of algorithms 2, as follows. \newline

	\begin{my}{1cm}{1cm}
		\rev{In particular, regarding experience $n$, the target-Q value $\hat{Q}_{i,n}^{\text{T}}$ represents the long-term QoE for action $\boldsymbol{a}_i(n)$ under state $\boldsymbol{s}_i(n)$. This value corresponds to the QoE observed in experience $n$, as well as the approximate expected upcoming QoE. 
			\textcolor{blue}{Based on the previous sample experiences $\mathcal{N}$, the EN computes the vector $\hat{\mathbf{Q}}_i^{\text{T}} = (\hat{Q}^{\text{T}}_{i,n})_{n \in \mathcal{N}}$ and trains the MD's neural network (in steps 11-21 of Algorithm ~\ref{alg:cap2}) to keep parameter vector $\theta^{\text{E}}_i$ in $\textit{Net}_i^{\text{E}}$ update for the MD's \textit{UpdateRequest}}. The key idea of updating $\textit{Net}_i^{\text{E}}$ is to minimize the disparity in Q-values between $\textit{Net}_i^{\text{E}}$ and $\textit{Net}_i^{\text{T}}$, as indicated by the following loss function:\\ \dots}
	\end{my}

	We have also revised algorithm 1 and 2, as below.\\

\begin{my}{0.5cm}{0.5cm}	
\rev{\begin{minipage}[b]{0.87\textwidth} 
	\begin{algorithm}[H] \caption{QECO Algorithm (Training Process)}\label{alg:cap2} \centering 
		\begin{algorithmic}[1] \renewcommand{\algorithmicrequire}{\textbf{\textcolor{blue}{Input:}}} \renewcommand{\algorithmicensure}{\textbf{\textcolor{blue}{Output:}}} \Require \textcolor{blue}{experience $(\boldsymbol{s}_i(t), \boldsymbol{a}_i(t), \boldsymbol{q}_i(t), \boldsymbol{s}_i(t+1))$ from MD $i \in \mathcal{I}$} \Ensure \textcolor{blue}{parameter vector $\theta_i^{\text{E}}$} 
	\end{algorithmic} 
\end{algorithm} 
\end{minipage}
\vspace{5mm}

\begin{minipage}[b]{0.87\textwidth} 
	\begin{algorithm}[H] \caption{QECO Algorithm (Offloading Decision)}\label{alg:cap2} \centering 
		\begin{algorithmic}[1] \renewcommand{\algorithmicrequire}{\textbf{Input:}} \renewcommand{\algorithmicensure}{\textbf{Output:}}\Require state space $\mathcal{S}$, action space $\mathcal{A}$
			\Ensure MD $i \in \mathcal{I}$ experience  \textcolor{blue}{ $(\hspace{-0.2mm}\boldsymbol{s}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{a}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{q}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{s}_i(\hspace{-0.2mm}t\hspace{-0.3mm}+\hspace{-0.3mm}\hspace{-0.2mm}1\hspace{-0.2mm}\hspace{-0.2mm})\hspace{-0.2mm})$}
		\end{algorithmic} 
	\end{algorithm} 
\end{minipage}}
\end{my}

\vspace{10mm}
	\item \underline{Reviewer's Comment}: 
	\textit{``The authors should open their experiments in github, so that other researchers can compare their work with other ones.''} \newline
	\underline{Authors' Reply}: To address the reviewer comment, we make our experiments more accessible by sharing our GitHub rerepository. We have added it into the end of first paragraph of Section V, as follows.
	\begin{my}{1cm}{1cm}
		\rev{Detailed settings regarding the neural networks and simulation can be found at our github repository. }
	\end{my}
	We have also provided repository URL link in the footnote of Page 8 as below.
	\begin{my}{1cm}{1cm}
		\rev{The code for reproducing the simulation results of this letter is available at\newline https://github.com/ImanRHT/QECO.} \newline
	\end{my}

\newpage
	\item \underline{Reviewer's Comment}: 
	\textit{``The following references closely related to the current work should be discussed or compared with the current work for completeness.''} \newline
		\begin{my}{1cm}{1cm}
		\rev{
			{\small
				\noindent\cite{b35} G. Wu, Z. Xu, H. Zhang, S. Shen, and S. Yu,  ``Multi-agent DRL for joint completion delay and energy consumption with queuing theory in MEC-based IIoT,'' in \textit{Journal of Parallel and Distributed Computing}, vol. 176, pp. 80–94, Jun. 2023.\\[6pt]
				\cite{b38} G. Wu, H. Wang, H. Zhang, Y. Zhao, S. Yu, and S. Shen, ``Computation offloading method using stochastic games for software-defined-network-based multiagent mobile edge computing,'' \textit{IEEE Internet of Things Journal}, vol. 10, no. 20, pp. 17620–17634, Oct. 2023.\\[6pt]
				\cite{b37} G. Wu, X. Chen, Z. Gao, H. Zhang, S. Yu, and S. Shen, ``Privacy-preserving offloading scheme in multi-access mobile edge computing based on MADRL,'' \textit{Journal of Parallel and Distributed Computing}, vol. 10, no. 1, pp. 451--460, Mar. 2022.\\[6pt]
				\cite{b39} G. Wu, X. Chen, Y. Shen, Z. Xu, H. Zhang, S. Shen, and S. Yu,``Combining Lyapunov optimization with Actor-Critic networks for privacy-aware IIoT computation offloading,'' in \textit{IEEE Internet of Things Journal}, 2024, Early Access\\[10pt]}\\}
	\end{my}

	\underline{Authors' Reply}:\\

	Ref

\end{enumerate}

\newpage

\section{Response to Reviewer 1}
\begin{enumerate}

	\item \underline{Reviewer's Comment}: \textit{``(a) The Introduction is verbose and confusing. (b) The authors should consider clarifying the relationship between task offloading and energy optimization in this paper.''} \newline

\underline{Authors' Reply}: (a) To address the reviewer comment, we have first summarized the explanation of the Internet of Things (IoT) applications, mobile edge computing (MEC), and the motivations of the proposed three-tier computing model. We have revised the first paragraph of Section I as follows.\\

\begin{my}{1cm}{1cm}
	\rev{The Internet of Things (IoT) applications (e.g., smart cities \cite{b1}, homes \cite{b3}, and augmented/virtual reality \cite{b11}) are mostly involved with computation-intensive and latency-sensitive tasks. Mobile edge computing (MEC) is a state-of-the-art computation paradigm to address the challenge of insufficient computing resources in IoT networks \cite{b35, b4}. By deploying the edge servers, nearby devices can offload their computation tasks. Dispatching those tasks that require a higher amount of energy will let devices save more energy \cite{b38}. However, as the computation tasks become more and more intensive, coordination with cloud servers will be inevitable \cite{b37}. The three-tier computing models consisting of cloud, edge, and IoT devices are introduced to overcome the aforementioned challenge \cite{b5,b6,b39,b40}. }\newline
\end{my}

We have also revised the second paragraph of Section I to better emphasize the role of the proposed system in overcoming the challenges of IoT systems.\\

\begin{my}{1cm}{1cm}
	\rev{In addition to their restricted computation resources, IoT devices usually have small battery capacities which is mainly due to their small form factor and the constraints of the production cost \cite{b1}.

	$\cdots$

By combining the advantages of MEC and WPC, the newly emerged wireless powered MEC (WPMEC) holds a major promise to overcome the fundamental hurdles in scalability of the IoT networks \cite{b9,b10,b30,b33}.}\newline

\end{my}

(b) Furthermore, we clarify the relationship between computation offloading and energy optimization. Note that in WPMEC systems, the energy for the operation of WDs is provided by the HAP. Thus, we formulate an optimization problem to minimize the total energy consumption of the HAP at the ET by jointly considering computation offloading, scheduling, and power allocation while guaranteeing the task completion and energy constraints. The following explanations have been added to Section I of the revised manuscript. \\

\begin{my}{1cm}{1cm}
	\rev{ 
		By deploying the edge servers, nearby devices can offload their computation tasks. Dispatching those tasks that require a higher amount of energy will let devices save more energy \cite{b38}.

		$\cdots$

However, due to the limitation of WET and the cost of ETs, reducing the energy consumption is crucial.

$\cdots$

It helps WDs save more energy and reduce the tasks' execution time, which consequently reduces the energy consumption of WPMEC system as WDs harvest energy from ETs.}\newline

\end{my}

We have also revised the first paragraph of Section III.A to address the reviewer comment. \\

\begin{my}{1cm}{1cm}
	\rev{In WPMEC systems, the energy for the operation of WDs is provided by the HAP.  Due to the high attenuation of WET over distances \cite{b8}, a considerable amount of energy is required to be provided for sustainable operation of WDs, which imposes a high cost to HAP. In this paper, we formulate an optimization problem to minimize the total energy consumption of the HAP at the ET by jointly considering computation offloading, scheduling, and power allocation while guaranteeing the task completion and energy constraints.} \newline
\end{my}

We hope the above changes make the introduction more concise and less confusing.\\

\item \underline{Reviewer's Comment}: \textit {``The authors introduce many works on computation offloading and energy consumption, however, the contributions of the paper are not clear.''} \newline

### 2024-09-14 Response/Response.tex

\underline{Authors' Reply}: We first clarify our contributions in comparison to the existing works. In the ETEM problem formulation, unlike other works in the WPMEC literature (e.g., \cite{b11,b13,b28}), we first consider a three-tier computing paradigm that includes wireless devices, edge servers, and the remote cloud server. This architecture helps in further scaling WPMEC systems in terms of computation capability. We also take the MEC server computation time into account to more accurately model the MEC servers. Another main contribution is considering task interdependencies to capture real-world applications. In the WiEnTM algorithm, we first exploit the bipartite graph matching to tackle the complexity of the combinatorial ETEM problem. With efficient parallelization, we then propose a low complexity algorithm that can solve ETEM in real-time.

In summary, the main contributions of our work are:

\begin{enumerate}
	\item Formulating ETEM problem for a three-tier wireless powered mobile edge computing system considering task interdependencies and MEC server computation time to minimize the energy consumption.
	\item Proposing WiEnTM offloading and scheduling algorithm that greatly enhances energy efficiency while imposing a logarithmic time complexity by leveraging parallel processing and bipartite graph matching. Therefore, the algorithm can easily accommodate the real-time requirements of an offloading scheme. In order to apply the matching algorithm to ETEM problem, we study the characteristics of the problem. We first reduce it into a simplified form (i.e., S-ETEM). Next, we introduce a design parameter $\beta_{v_d^u}$ for each subtask $v_d^u\in\mathcal{V}_d$ of WD $\mathcal{D}^u$ and episode $u\in\mathcal{U}$ to decompose it into a number of independent problems (i.e., DS-ETEM).
	\item Evaluating the performance of WiEnTM in different scenarios and comparing to other state-of-the-art algorithms.
\end{enumerate}

In Section I of the revised manuscript, we have further explained the related works and clarified our main contributions as follows.\\

\begin{my}{1cm}{1cm}
	\rev{
		\textcolor{blue}{In \cite{b39}, authors proposed a scheme that aims to minimize the total cost in terms of energy and delay for a three-tier cloud-edge-IoT system. Gao \textit{et al.} in \cite{b40} proposed an offloading algorithm to minimize an objective called the energy time cost for a three-tier network. Although \cite{b5}, \cite{b39}, and \cite{b40} all benefit from a computationally-scalable three-tier system, IoT devices still rely on battery energy and hence lack the sustainability feature of WPMEC systems.}

		$\cdots$

		However, the proposed system model is oversimplified and thus less applicable to real-world scenarios.\\
	}
\end{my}

To make the contributions more clear, we have made the following changes to Section I of the revised manuscript.\\

\begin{my}{1cm}{1cm}
	\rev{\textcolor{blue}{By considering the challenges of the aforementioned works, the following questions arise:}
\begin{enumerate}
	\item \textcolor{blue}{\textit{How can we take advantage of cloud computing in addition to MEC to meet different requirements of IoT applications?}}
	\item \textcolor{blue}{\textit{How can we provide RF energy to enable the battery-less IoT devices operate seamlessly?}}
	\item \textcolor{blue}{\textit{What would be the optimal offloading decision when considering the subtasks' interdependencies?}}
\end{enumerate}

$\cdots$

		\begin{enumerate}
			\item \textcolor{blue}{\textit{Problem formulation}: We formally define the mixed-integer ET's energy minimization (ETEM) problem by deciding on offloading, WET time, and computation scheduling of subtasks for a multi-user three-tier WPMEC system} considering task interdependencies and MEC server computation time.
			\item \textcolor{blue}{\textit{Algorithm design}: We propose wireless energy transmission minimization (WiEnTM) algorithm based on bipartite graph matching. We first study the properties of the problem to decompose it into individual problems for each subtask to make it suitable for the matching algorithm.} By efficiently utilizing parallel processing on decomposed problems, we prove that our proposed algorithm has a logarithmic time complexity with respect to the network size.
			\item \textcolor{blue}{\textit{Performance evaluation}: Extensive numerical experiments are carried out to evaluate the proposed algorithm. Our experiments show major reduction in the WDs' required energy in comparison with baseline offloading policies.} The algorithm also reduces the energy consumption by 34\% for large tasks compared to an existing work \cite{b13}.\\
		\end{enumerate}
	}
\end{my}

\item \underline{Reviewer's Comment}: \textit {``Experiments need to be improved. WiEnTm proposed by this paper only compares time with WPMEC- [16]. However, WiEnTm is an energy optimization algorithm, and the main purpose of this paper is energy efficiency. I would like to know the energy performance of WiEnTm compared to other works, but it is not reflected in the paper. In addition, if authors want to show the performance of the proposed mechanism in various aspects, then it is necessary to compare it with state-of-the-art works.''} \newline

\underline{Authors' Reply}: To address the reviewer's comment, we have included Fig. \ref{fig:7r} in Section V of the revised manuscript. This figure shows the energy consumption of our proposed algorithm in comparison to a state-of-the-art work in the literature. We have also updated the following paragraph in Section V of the revised manuscript to explain the results.\newline
\begin{my}{1cm}{1cm}
	\rev{We further investigate the performance of our proposed WiEnTM algorithm by evaluating the ET's transmitted energy in comparison to that of \cite{b13}. Figs. \ref{fig:7ar} and \ref{fig:7br} illustrate the effect of the task's CPU cycles and the task size (i.e., the number of input/output bits), respectively. The results show that by using WiEnTM, the ET consumes up to $34\%$ less energy compared to the algorithm in \cite{b13}.\\
	}

\end{my}

\setcounter{figure}{7}
\begin{figure}
	\centering
	\begin{subfigure}[b]{.43\textwidth}
		\centering
		\includegraphics[width=\linewidth]{simulation2_a.pdf}
		\caption{} \label{fig:7ar}
	\end{subfigure}
	\begin{subfigure}[b]{.43\textwidth}
		\centering
		\includegraphics[width=\linewidth]{simulation2_b.pdf}
		\caption{} \label{fig:7br}
	\end{subfigure}

	\caption{\textcolor{blue}{Comparison of ET's transmitted energy between WiEnTM and the algorithm proposed in \cite{b13} for different a) task's CPU cycles (i.e., $\sum_{v_d\in\mathcal{V}_d}C_{v_d}$) and, b) task's internal input/output bits (i.e., $\sum_{v_d^i,v_d^j\in\mathcal{V}_d}N_{v_d^i,v_d^j}$).}} \label{fig:7r}
\end{figure}

 \setstretch{1.2}

\end{enumerate}

We highly appreciate the reviewer for the comments and suggestions. We hope that we have properly addressed these issues.

\section{Response to Reviewer 2}
\begin{enumerate}

\item \underline{Reviewer's Comment}: \textit{``It would be great if the authors provided one or multiple tables of key symbols and their corresponding description in the appendix or paper body instead of describing them in the text. This way is much easier to refer to the symbols.''} \newline

\underline{Authors' Reply}: In the revised manuscript, we have added the following table which includes the key notations alongside their descriptions.

\setcounter{table}{0}

\begin{my}{0cm}{0cm}
	\rev{
		\begin{table}[h]
			\centering
			\caption{\textcolor{blue}{List of key notations}}
			\label{table2}
			{\color{blue}\begin{tabular}{ |p{2cm}|p{12cm}|  }
				\hline
				\textbf{Symbol} & \textbf{Description} \\
				\hline
				$x^{\text{L}}_{v_d^u}, x^{\text{M}}_{v_d^u}, x^{\text{C}}_{v_d^u}$ & Binary offloading decisions \\
				$\tau_{1,v_d^u}$ & Length of scheduled time for data transmission of subtask $v_d^u$ \\
				$\tau_{2,v_d^u}$ & Length of scheduled time for execution of subtask $v_d^u$\\
				$\tau_{3,v_d^u}$ & Length of scheduled time for retrieving the result of subtask $v_d^u$ \\
				$\tau_0^u$ & WET time in episode $u$\\
				$p^{u}$ & ET's power in episode $u$ \\
				$\Gamma^u$ & Length of episode $u$ \\
				$\mu_{v_d^u}$ & Response time of cloud server for subtask $v_d^u$ \\
				$C_{v_d^u}$ & Number of CPU cycles required for subtask $v_d^u$ \\
				$N_{i,j}$ & Number of bits required to transmit the result of subtask $i$ and $j$ \\
				$g_d$ & Channel gain between WD $d$ and ET \\
				$h_d$ & Channel gain between WD $d$ and MEC server \\
				$\sigma^2$ & Noise power at the HAP \\
				$\eta_d$ & Energy harvesting efficiency of WD $d$ \\
				$\zeta_{d}$ & CPU's effective switched capacitance of WD $d$ \\
				$r_{t,v_d^u}$ & Virtual resource for tier $t$ and subtask $v_d^u$ \\
				$F^{\text{M},\max}$ & Maximum CPU frequency of MEC server \\
				$F^{\text{L},\max}_{d}$ & Maximum CPU frequency of WD $d$ \\
				$P^{\text{ET},\max}$ & ET's maximum transmission power \\
				$P^{\text{AP},\max}$ & AP's maximum transmission power \\
				$P^{\text{WD},\max}_d$ & Maximum transmission power of WD $d$ \\
				$D$ & Number of WDs \\
				$V_d$ & Number of subtasks of WD $d$ \\
				$B_d$ & Bandwidth of WD $d$ \\
				$\mathcal{D}$, $\mathcal{D}^u$ & Set of WDs \\ 
				$\mathcal{U}$ & Set of episodes \\
				$\mathcal{V}_d$ & Set of subtasks of WD $d$ \\
				$\mathcal{R}^{\text{virt}}$ & Set of virtual resources \\
				$\mathcal{I}_{v_d^u}$ & Set of episodes associated to executing prerequisite subtasks of the subtask $v_d^u$ \\
				$\mathcal{J}_{v_d^u}$ & Set of episodes associated to executing subtasks with the subtask $v_d^u$ as their prerequisite \\
				\hline
			\end{tabular}}
	\end{table}}
\end{my}

 \setstretch{1.2}

\end{enumerate}

We would like to gratefully thank the reviewer for the valuable suggestion and comment. We hope that we have addressed this comment satisfactorily. \newpage

\section{Response to Reviewer 3}
\begin{enumerate}

\item \underline{Reviewer's Comment}: \textit{``Although the optimization objective of the investigated problem is to minimize energy consumption of the HAP, the time consumption for all subtasks generated by WDs still should be constrained. Otherwise, the QoS of latency-sensitive tasks cannot be guaranteed by the proposed algorithms.''} \newline

\underline{Authors' Reply}: The time consumption for all subtasks generated by WDs are indeed constrained in our work. With the introduction of episodes, we have simultaneously addressed the requirements of harvest-then-offload mechanism and the subtasks' deadlines. Constraint (\ref{eq9}) applies a hard deadline $\Gamma^u$ on each episode $u\in\mathcal{U}$ (i.e., a cycle of subtasks' executions) which is obtained based on the deadline of subtasks. In order to clarify this, we have included the following sentences in Section III of the revised manuscript. \newline

\begin{my}{1cm}{1cm}
\rev{	
	It is worth noting that inequality (\ref{eq9}) also enforces a hard deadline for each cycle of subtasks' execution in each episode. Thus, the total execution time of each task generated by WDs is constrained. This way, we can address the requirements of latency-sensitive tasks as well.
}\newline
\end{my}

Furthermore, we have included the following sentences to better illustrate the intention behind defining an \textit{episode} in Section II of the revised manuscript.\\

\begin{my}{1cm}{1cm}
	\rev{We regard a complete cycle of executing a single subtask for all WDs having a candidate subtask as an \textit{episode}. Each episode jointly models the harvest-then-offload timing, subtasks' deadlines, and TDMA scheduling of WDs.
	}\newline
\end{my}

\item \underline{Reviewer's Comment}: \textit {``(a) The definition of an “episode” is not stated clearly. (b) The first question is how to decide the length of an episode? (c) Since the length of an episode will affect the performance of scheduling, it should be analyzed theoretically. (d) Besides, how to decide the number of episodes?''} \newline

\underline{Authors' Reply}: We address each of the above comments one by one.\newline

(a) In Section II of the revised manuscript, we have first clarified the definition of an episode as follows.\\

\begin{my}{1cm}{1cm}
\rev{We regard a complete cycle of executing a single subtask for all
	WDs having a candidate subtask as an \textit{episode}. Each episode
	jointly models the harvest-then-offload timing, subtasks' deadlines, and TDMA scheduling of WDs.}\newline

\end{my}

(b) An episode is a complete cycle of subtasks' execution, including harvest-then-offload timing and subtasks' deadlines. Therefore, similar to other works in the literature of WPMEC (e.g., \cite{b2,b13,b28}), we consider that the length of an episode is directly related to subtasks' deadlines. In the revised manuscript, we have included the following paragraph in Section II to discuss an approach to calculate the length of an episode.\newline

\begin{my}{1cm}{1cm}
	\rev{Now that we have introduced the network model, we need to provide an approach to calculate the length of episode $\Gamma$. As stated earlier, each episode reflects the requirements of the harvest-then-offload timing and subtask deadlines. Therefore, $\Gamma$ is directly related to the individual subtask deadlines being executed in that episode. In other words, $\Gamma$ can be calculated as the summation of the subtasks' deadlines. In the next section, we will calculate the length of each episode.}\newline

\end{my}

(c) The length of an episode is present in inequality constraint (\ref{eq9}). Thus, a longer episode (i.e., the subtasks' deadlines) will enlarge the feasible region of the ETEM optimization problem and enhances the optimal solution and results in less energy consumption. In Section V, we have used this intuition to propose the adaptive approach for calculating the $\beta_{v_d^u}$ parameters. To further clarify, we have included the following sentences in Section III of the revised manuscript.\newline

\begin{my}{1cm}{1cm}
	\rev{Also, it can be concluded that $\Gamma^u$ is a key factor in the optimal value of the ETEM problem. A longer episode (i.e., larger $\Gamma^u$) provides more time for execution of the tasks. In fact, this will enlarge the feasible region of the ETEM optimization problem and enhances the energy-efficiency of the algorithm.}\newline
\end{my}

(d) The number of episodes corresponds to the time horizon of the problem. We defined the horizon to be the time required to accomplish a task on all WDs. Therefore, as long as there exists a subtask to be executed on WDs, a new episode will be required. This will result in having $\max_{d\in\mathcal{D}}V_d$ episodes. In the revised manuscript, we have updated the following sentences to further clarify how the number of required episodes (i.e., $U$) is calculated.\\

\begin{my}{1cm}{1cm}
	\rev{We denote $\mathcal{U}\triangleq\{0,...,U-1\}$ as the set of episodes, where $U\triangleq\max_{d\in\mathcal{D}}V_d$  indicates the number of episodes. Note that $V_d$ is obtained from the call graph of the corresponding task. \newline}
\end{my}

\item \underline{Reviewer's Comment}: \textit {``There are too many symbols in this paper. It is hard for readers to quickly find the meaning of each symbol. A symbol table should be added to improve the readability of this paper.''} \newline

\underline{Authors' Reply}: In the revised manuscript, we have added Table \ref{table3} which includes the key notations alongside their descriptions. \newline

\setcounter{table}{0}

\begin{my}{1cm}{1cm}
	\rev{		\begin{table}[h]
			\centering
			\caption{\textcolor{blue}{List of key notations}}
			\label{table3}
			{\color{blue}\begin{tabular}{ |p{2cm}|p{12cm}|  }
				\hline
				\textbf{Symbol} & \textbf{Description} \\
				\hline
				$x^{\text{L}}_{v_d^u}, x^{\text{M}}_{v_d^u}, x^{\text{C}}_{v_d^u}$ & Binary offloading decisions \\
				$\tau_{1,v_d^u}$ & Length of scheduled time for data transmission of subtask $v_d^u$ \\
				$\tau_{2,v_d^u}$ & Length of scheduled time for execution of subtask $v_d^u$\\
				$\tau_{3,v_d^u}$ & Length of scheduled time for retrieving the result of subtask $v_d^u$ \\
				$\tau_0^u$ & WET time in episode $u$\\
				$p^{u}$ & ET's power in episode $u$ \\
				$\Gamma^u$ & Length of episode $u$ \\
				$\mu_{v_d^u}$ & Response time of cloud server for subtask $v_d^u$ \\
				$C_{v_d^u}$ & Number of CPU cycles required for subtask $v_d^u$ \\
				$N_{i,j}$ & Number of bits required to transmit the result of subtask $i$ and $j$ \\
				$g_d$ & Channel gain between WD $d$ and ET \\
				$h_d$ & Channel gain between WD $d$ and MEC server \\
				$\sigma^2$ & Noise power at the HAP \\
				$\eta_d$ & Energy harvesting efficiency of WD $d$ \\
				$\zeta_{d}$ & CPU's effective switched capacitance of WD $d$ \\
				$r_{t,v_d^u}$ & Virtual resource for tier $t$ and subtask $v_d^u$ \\
				$F^{\text{M},\max}$ & Maximum CPU frequency of MEC server \\
				$F^{\text{L},\max}_{d}$ & Maximum CPU frequency of WD $d$ \\
				$P^{\text{ET},\max}$ & ET's maximum transmission power \\
				$P^{\text{AP},\max}$ & AP's maximum transmission power \\
				$P^{\text{WD},\max}_d$ & Maximum transmission power of WD $d$ \\
				$D$ & Number of WDs \\
				$V_d$ & Number of subtasks of WD $d$ \\
				$B_d$ & Bandwidth of WD $d$ \\
				$\mathcal{D}$, $\mathcal{D}^u$ & Set of WDs \\ 
				$\mathcal{U}$ & Set of episodes \\
				$\mathcal{V}_d$ & Set of subtasks of WD $d$ \\
				$\mathcal{R}^{\text{virt}}$ & Set of virtual resources \\
				$\mathcal{I}_{v_d^u}$ & Set of episodes associated to executing prerequisite subtasks of the subtask $v_d^u$ \\
				$\mathcal{J}_{v_d^u}$ & Set of episodes associated to executing subtasks with the subtask $v_d^u$ as their prerequisite \\
				\hline
			\end{tabular}}
	\end{table}}
\end{my}

\item \underline{Reviewer's Comment}: \textit {``In the proposed MGW algorithm, how could all executions in line 4 to line 17 proceed parallelly? As the authors mentioned that all subtasks have dependencies, one subtask should be computed based on the results of other subtasks. In this case, how could the weights be assigned parallelly? A more delicate methods for dealing the dependencies among subtasks should be provided.''} \newline
